---
title: "MHotchkiss - Final Project - Statistical Analysis"
author: "Michelle Hotchkiss"
date: "19/03/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Data Set Up

Load all necessary libraries.

```{r}
library(tidyverse)
library(ggforce)
library(lme4)
library(lmerTest)
```

Load data into R and check structure.

```{r}
syrup_vol_data <- read.csv("data-raw/volume24_corr.csv")

str(syrup_vol_data)
```

Want to recategorize md_id, sc_id, age, exposure, and treatment as factors.

```{r}
syrup_vol_data$mc_id <- as.factor(syrup_vol_data$mc_id)
syrup_vol_data$sc_id <- as.factor(syrup_vol_data$sc_id)
syrup_vol_data$age <- as.factor(syrup_vol_data$age)
syrup_vol_data$exposure <- as.factor(syrup_vol_data$exposure)
syrup_vol_data$treatment <- as.factor(syrup_vol_data$treatment)
```

Then re-order the treatment and exposure levels.

```{r}
syrup_vol_data$treatment <- factor(syrup_vol_data$treatment, levels = c("Control", "DMSO", "1ppb", "10 ppb", "100ppb", "800ppb", "Sacrifice"))
syrup_vol_data$exposure <- factor(syrup_vol_data$exposure, levels = c("pre", "during", "post"))
```

#### Filtering dataset for analysis

Made permanent dataset without Day -6, Sacrifice treatment, or Ages 7 and 9. Also made new variable for day coded as a factor to examine if any days are significantly different from one another.

Notes: Day -6 has been removed as this is the first day of the experiment and therefore there is no amount consumed for the past 24 hours. The Sacrifice treatment is removed because microcolonies used in this treatment were sacrificed on Day 5, and therefore have no data for Days 6-14. The age group Age 7 (7 week old bees) is removed as these samples were taken as part of a contingency plan that ultimately was not used.

```{r}
syrup_vol_data_fil <-
  syrup_vol_data %>% 
  filter(!is.na(volume24_corr)) %>% 
  filter(!(day=="-6")) %>% 
  filter(!(treatment=="Sacrifice")) %>% 
  filter(!(age=="7")) %>% 
  filter(!(age=="9"))

syrup_vol_data_fil$day_fac <- as.factor(syrup_vol_data_fil$day)

str(syrup_vol_data_fil)
```

## Preliminary Data Visualisation

#### Histogram of Corrected Daily Volumes

```{r}
syrup_vol_data_fil %>% 
  ggplot((aes(volume24_corr))) +
           geom_histogram(bins = 10)
```

Data appears relatively normally distributed.

#### Volume of Syrup Consumed in the Past 24h vs. Day, coloured by Treatment, faceted by Age

```{r}
syrup_vol_data_fil %>% 
  group_by(treatment, day, age) %>% 
  summarise(mean = mean(volume24_corr), se = (sd(volume24_corr)/sqrt(10))) %>% 
  ggplot(aes(day, mean, color=treatment)) +
  geom_line()+
  geom_point()+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2,
                 position=position_dodge(0.05))+
  theme_classic() +
  theme(
    text = element_text(size = 14), 
    axis.title.x=element_blank(),
    axis.text.x = element_text(vjust=0.3, size = 12, color="black"), 
    axis.ticks.x=element_blank(),
    axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
    axis.text.y = element_text(color="black", size = 10),
    strip.placement = "outside", 
    strip.text.x = element_text( #text in facet labels
      size = 12, color = "black", face = "bold"),
    strip.background = element_rect(#background of facet labels
      color="white", fill="#ffffff", size=1.5),
    panel.spacing.y = unit(2, "lines"),
    legend.position = "right")+
  
    scale_color_viridis_d(name = "Treatment", direction = -1)+
    scale_y_continuous(name ="Average Volume of Syrup \nConsumed Over 24h (mL)")+
  facet_wrap(~age)
```

## Linear Mixed Models

#### Linear Mixed Model Selection

###### Model1

```{r}
lm_1 <- lmer(volume24_corr ~ treatment*day_fac*age + (1|sc_id/mc_id), data=syrup_vol_data_fil)
```

No errors for model 1.

Look at summary.

```{r}
summary(lm_1)
```

Perform an ANOVA (Type III) to determine the significance of the fixed effects. Note: I am including my nested random effects in my model to account for inherent non-independence in my experimental design. Use `r ranova` to determine significance of random effects.

```{r}
anova(lm_1) #note: this is lmerTest anova which, in this case, is a type III anova for fixed-effects terms with the Satterthwaite method for denominator degrees of freedom

ranova(lm_1)
```

Based on ANOVA, fixed effects `r day_fac`, `r age`, and `r day_fac:age` are significant (p < 0.05). All other fixed factors are insignificant. Random effects are also significant. Most importantly, no effects have p-values that are "borderline significant" (i.e., close to the arbitrary 0.05 cutoff). Therefore, I will code a second model keeping only the significant terms.

###### Model 2

```{r}
lm_2 <- lmer(volume24_corr ~ day_fac + age + day_fac:age + (1|sc_id/mc_id), data=syrup_vol_data_fil)
```

No errors for model 2.

Summary and ANOVA for linear mixed model 2.

```{r}
summary(lm_2)
anova(lm_2)
ranova(lm_2)
```

## Test assumptions on Linear Mixed Model 2.

#### Assumption 1: Residuals are normally distributed.

```{r}
par(mfrow = c(1, 2)) # multiple graphs in a window
qqnorm(residuals(lm_2)) 
qqline(residuals(lm_2))
hist(resid(lm_2)) 
```

QQplot is heavy-tailed, but the histogram looks Gaussian.

As a follow-up, will run formal tests.

```{r}
shapiro.test(residuals(lm_2))
```

Formal test confirms that the normality assumption is violated. HOWEVER, Shapiro-Wilk test is very sensitive and linear mixed models are reasonably robust to violations of non-normality [@Knief2018; @Schielzeth2020].

#### Assumption 2: Homscedasticty (variance of residuals is constant across covariates)

```{r}
plot(lm_2)
```

Residuals appear to be evenly distributed above and below the line.

#### Assumption 3: Random effects have a Gaussian distribution

```{r}
r1 <- as.data.frame(ranef(lm_2, condVar = TRUE))
par(mfrow = c(1, 2))
hist(r1$condval)
qqnorm(r1$condval)
qqline(r1$condval)

str(r1)
```

Histogram and QQ line are actually pretty good!

#### Assumption 4: Residual variance is constant across all levels of a random effect

```{r}
r1 <- r1[order(r1$condval), ] # sorting the BLUPs
ggplot(r1, aes(y = grp, x = condval)) +
  geom_point() +
  geom_pointrange(
    aes(xmin = condval - condsd * 1.96, xmax = condval + condsd * 1.96)
  ) +
  geom_vline(aes(xintercept = 0, color = "red")) +
  theme_classic() +
  theme(legend.position = "none")
```

Widths of bars all appear to be equal.

## Post-hoc Tests and Figures

#### Set Up

Load libraries for post-hoc tests.

```{r}
library(emmeans)
library(multcompView)
```

#### Generate Comparison List

To create the list, I first generated a list of marginal means for all `r day` and `r age` combinations.

```{r}
lm_2_posthoc_means <- emmeans(lm_2, specs = ~day_fac:age)
lm_2_posthoc_means
```

I then assigned each marginal mean to a vector where 1 was its place in the list of marginal means and 0 was used in every other spot.

```{r}
#Define what each day/age combination is in the vector

DN51 = c(1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

DN41 = c(0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

DN31 = c(0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

DN21 = c(0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

DN11 = c(0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D01 = c(0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D11 = c(0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D21 = c(0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D31 = c(0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D41 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D51 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D61 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D71 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D81 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D91 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D101 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D111 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D121 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D131 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D141 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)


DN53 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

DN43 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

DN33 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

DN23 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

DN13 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D03 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D13 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D23 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D33 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D43 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0,0, 0, 0, 0, 0, 0, 0, 0, 0)

D53 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0)

D63 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0)

D73 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0)

D83 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0)

D93 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0)

D103 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0)

D113 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0)

D123 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0)

D133 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0)

D143 = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1)
```

I then generated a named list of all contrasts that I was interested in making.

```{r}

pwpp_comparisons <- 
    list("-5 1 to -4 1"= DN51-DN41,
         "-5 1 to -3 1" = DN51-DN31,
         "-5 1 to -2 1" = DN51-DN21,
         "-5 1 to -1 1" = DN51-DN11,
         "-5 1 to 0 1" = DN51-D01,
         "-5 1 to 1 1" = DN51-D11,
         "-5 1 to 2 1" = DN51-D21,
         "-5 1 to 3 1" = DN51-D31,
         "-5 1 to 4 1" = DN51-D41,
         "-5 1 to 5 1" = DN51-D51,
         "-5 1 to 6 1" = DN51-D61,
         "-5 1 to 7 1" = DN51-D71,
         "-5 1 to 8 1" = DN51-D81,
         "-5 1 to 9 1" = DN51-D91,
         "-5 1 to 10 1" = DN51-D101,
         "-5 1 to 11 1" = DN51-D111,
         "-5 1 to 12 1" = DN51-D121,
         "-5 1 to 13 1" = DN51-D131,
         "-5 1 to 14 1" = DN51-D141,
         "-5 1 to -5 3" = DN51-DN53,
         "-4 1 to -3 1" = DN41-DN31,
         "-4 1 to -2 1" = DN41-DN21,
         "-4 1 to -1 1" = DN41-DN11,
         "-4 1 to 0 1" = DN41-D01,
         "-4 1 to 1 1" = DN41-D11,
         "-4 1 to 2 1" = DN41-D21,
         "-4 1 to 3 1" = DN41-D31,
         "-4 1 to 4 1" = DN41-D41,
         "-4 1 to 5 1" = DN41-D51,
         "-4 1 to 6 1" = DN41-D61,
         "-4 1 to 7 1" = DN41-D71,
         "-4 1 to 8 1" = DN41-D81,
         "-4 1 to 9 1" = DN41-D91,
         "-4 1 to 10 1" = DN41-D101,
         "-4 1 to 11 1" = DN41-D111,
         "-4 1 to 12 1" = DN41-D121,
         "-4 1 to 13 1" = DN41-D131,
         "-4 1 to 14 1" = DN41-D141,
         "-4 1 to -4 3" = DN41-DN43,
         "-3 1 to -2 1" = DN31-DN21,
         "-3 1 to -1 1" = DN31-DN11,
         "-3 1 to 0 1" = DN31-D01,
         "-3 1 to 1 1" = DN31-D11,
         "-3 1 to 2 1" = DN31-D21,
         "-3 1 to 3 1" = DN31-D31,
         "-3 1 to 4 1" = DN31-D41,
         "-3 1 to 5 1" = DN31-D51,
         "-3 1 to 6 1" = DN31-D61,
         "-3 1 to 7 1" = DN31-D71,
         "-3 1 to 8 1" = DN31-D81,
         "-3 1 to 9 1" = DN31-D91,
         "-3 1 to 10 1" = DN31-D101,
         "-3 1 to 11 1" = DN31-D111,
         "-3 1 to 12 1" = DN31-D121,
         "-3 1 to 13 1" = DN31-D131,
         "-3 1 to 14 1" = DN31-D141,
         "-3 1 to -3 3" = DN31-DN33,
         "-2 1 to -1 1" = DN21-DN11,
         "-2 1 to 0 1" = DN21-D01,
         "-2 1 to 1 1" = DN21-D11,
         "-2 1 to 2 1" = DN21-D21,
         "-2 1 to 3 1" = DN21-D31,
         "-2 1 to 4 1" = DN21-D41,
         "-2 1 to 5 1" = DN21-D51,
         "-2 1 to 6 1" = DN21-D61,
         "-2 1 to 7 1" = DN21-D71,
         "-2 1 to 8 1" = DN21-D81,
         "-2 1 to 9 1" = DN21-D91,
         "-2 1 to 10 1" = DN21-D101,
         "-2 1 to 11 1" = DN21-D111,
         "-2 1 to 12 1" = DN21-D121,
         "-2 1 to 13 1" = DN21-D131,
         "-2 1 to 14 1" = DN21-D141,
         "-2 1 to -2 3" = DN21-DN23,
         "-1 1 to 0 1" = DN11-D01,
         "-1 1 to 0 1" = DN11-D11,
         "-1 1 to 2 1" = DN11-D21,
         "-1 1 to 3 1" = DN11-D31,
         "-1 1 to 4 1" = DN11-D41,
         "-1 1 to 5 1" = DN11-D51,
         "-1 1 to 6 1" = DN11-D61,
         "-1 1 to 7 1" = DN11-D71,
         "-1 1 to 8 1" = DN11-D81,
         "-1 1 to 9 1" = DN11-D91,
         "-1 1 to 10 1" = DN11-D101,
         "-1 1 to 11 1" = DN11-D111,
         "-1 1 to 12 1" = DN11-D121,
         "-1 1 to 13 1" = DN11-D131,
         "-1 1 to 14 1" = DN11-D141,
         "-1 1 to -1 3" = DN11-DN13,
        "0 1 to 1 1" = D01-D11,
        "0 1 to 2 1" = D01-D21,
        "0 1 to 3 1" = D01-D31,
        "0 1 to 4 1" = D01-D41,
        "0 1 to 5 1" = D01-D51,
        "0 1 to 6 1" = D01-D61,
        "0 1 to 7 1" = D01-D71,
        "0 1 to 8 1" = D01-D81,
        "0 1 to 9 1" = D01-D91,
        "0 1 to 10 1" = D01-D101,
        "0 1 to 11 1" = D01-D111,
        "0 1 to 12 1" = D01-D121,
        "0 1 to 13 1" = D01-D131,
        "0 1 to 14 1" = D01-D141,
        "0 1 to 0 3" = D01-D03,
        "1 1 to 2 1" = D11-D21,
        "1 1 to 3 1" = D11-D31,
        "1 1 to 4 1" = D11-D41,
        "1 1 to 5 1" = D11-D51,
        "1 1 to 6 1" = D11-D61,
        "1 1 to 7 1" = D11-D71,
        "1 1 to 8 1" = D11-D81,
        "1 1 to 9 1" = D11-D91,
        "1 1 to 10 1" = D11-D101,
        "1 1 to 11 1" = D11-D111,
        "1 1 to 12 1" = D11-D121,
        "1 1 to 13 1" = D11-D131,
        "1 1 to 14 1" = D11-D141,
        "1 1 to 1 3" = D11-D13,
        "2 1 to  3 1" = D21-D31,
        "2 1 to  4 1" = D21-D41,
        "2 1 to  5 1" = D21-D51,
        "2 1 to  6 1" = D21-D61,
        "2 1 to  7 1" = D21-D71,
        "2 1 to  8 1" = D21-D81,
        "2 1 to  9 1" = D21-D91,
        "2 1 to  10 1" = D21-D101,
        "2 1 to  11 1" = D21-D111,
        "2 1 to  12 1" = D21-D121,
        "2 1 to  13 1" = D21-D131,
        "2 1 to  14 1" = D21-D141,
        "2 1 to 2 3" = D21-D23,
        "3 1 to  4 1" = D31-D41,
        "3 1 to  5 1" = D31-D51,
        "3 1 to  6 1" = D31-D61,
        "3 1 to  7 1" = D31-D71,
        "3 1 to  8 1" = D31-D81,
        "3 1 to  9 1" = D31-D91,
        "3 1 to  10 1" = D31-D101,
        "3 1 to  11 1" = D31-D111,
        "3 1 to  12 1" = D31-D121,
        "3 1 to  13 1" = D31-D131,
        "3 1 to  14 1" = D31-D141,
        "3 1 to 3 3" = D31-D33,
        "4 1 to  5 1" = D41-D51,
        "4 1 to  6 1" = D41-D61,
        "4 1 to  7 1" = D41-D71,
        "4 1 to  8 1" = D41-D81,
        "4 1 to  9 1" = D41-D91,
        "4 1 to  10 1" = D41-D101,
        "4 1 to  11 1" = D41-D111,
        "4 1 to  12 1" = D41-D121,
        "4 1 to  13 1" = D41-D131,
        "4 1 to  14 1" = D41-D141,
        "4 1 to 4 3" = D41-D43,
        "5 1 to  6 1" = D51-D61,
        "5 1 to  7 1" = D51-D71,
        "5 1 to  8 1" = D51-D81,
        "5 1 to  9 1" = D51-D91,
        "5 1 to  10 1" = D51-D101,
        "5 1 to  11 1" = D51-D111,
        "5 1 to  12 1" = D51-D121,
        "5 1 to  13 1" = D51-D131,
        "5 1 to  14 1" = D51-D141,
        "5 1 to 5 3"= D51-D53,
        "6 1 to  7 1" = D61-D71,
        "6 1 to  8 1" = D61-D81,
        "6 1 to  9 1" = D61-D91,
        "6 1 to  10 1" = D61-D101,
        "6 1 to  11 1" = D61-D111,
        "6 1 to  12 1" = D61-D121,
        "6 1 to  13 1" = D61-D131,
        "6 1 to  14 1" = D61-D141,
        "6 1 to 6 3" = D61-D63,
        "7 1 to  8 1" = D71-D81,
        "7 1 to  9 1" = D71-D91,
        "7 1 to  10 1" = D71-D101,
        "7 1 to  11 1" = D71-D111,
        "7 1 to  12 1" = D71-D121,
        "7 1 to  13 1" = D71-D131,
        "7 1 to  14 1" = D71-D141,
        "7 1 to 7 3" = D71-D73,
        "8 1 to 9 1" = D81-D91,
        "8 1 to 10 1" = D81-D101,
        "8 1 to 11 1" = D81-D111,
        "8 1 to 12 1" = D81-D121,
        "8 1 to 13 1" = D81-D131,
        "8 1 to 14 1" = D81-D141,
        "8 1 to 8 3" = D81-D83,
        "9 1 to  10 1" = D91-D101,
        "9 1 to  11 1" = D91-D111,
        "9 1 to  12 1" = D91-D121,
        "9 1 to  13 1" = D91-D131,
        "9 1 to  14 1" = D91-D141,
        "9 1 to 9 3" = D91-D93,
        "10 1 to  11 1" = D101-D111,
        "10 1 to  12 1" = D101-D121,
        "10 1 to  13 1" = D101-D131,
        "10 1 to  14 1" = D101-D141,
        "10 1 to 10 3" = D101-D103,
        "11 1 to  12 1" = D111-D121,
        "11 1 to  13 1" = D111-D131,
        "11 1 to  14 1" = D111-D141,
        "11 1 to 11 3" = D111-D113,
        "12 1 to  13 1" = D121-D131,
        "12 1 to  14 1" = D121-D141,
        "12 1 to 12 3" = D121-D123,
        "13 1 to 14 1" = D131-D141,
        "13 1 to 13 3" = D131-D133,
        "14 1 to 14 3" = D141-D143,
        "-5 3 to  -4 3" = DN53-DN43,
        "-5 3 to  -3 3" = DN53-DN33,
        "-5 3 to  -2 3" = DN53-DN23,
        "-5 3 to  -1 3" = DN53-DN13,
        "-5 3 to  0 3" = DN53-D03,
        "-5 3 to  1 3" = DN53-D13,
        "-5 3 to  2 3" = DN53-D23,
        "-5 3 to  3 3" = DN53-D33,
        "-5 3 to  4 3" = DN53-D43,
        "-5 3 to  5 3" = DN53-D53,
        "-5 3 to  6 3" = DN53-D63,
        "-5 3 to  7 3" = DN53-D73,
        "-5 3 to  8 3" = DN53-D83,
        "-5 3 to  9 3" = DN53-D93,
        "-5 3 to  10 3" = DN53-D103,
        "-5 3 to  11 3" = DN53-D113,
        "-5 3 to  12 3" = DN53-D123,
        "-5 3 to  13 3" = DN53-D133,
        "-5 3 to  14 3" = DN53-D143,
        "-4 3 to  -3 3" = DN43-DN33,
        "-4 3 to  -2 3" = DN43-DN23,
        "-4 3 to  -1 3" = DN43-DN13,
        "-4 3 to  0 3" = DN43-D03,
        "-4 3 to  1 3" = DN43-D13,
        "-4 3 to  2 3" = DN43-D23,
        "-4 3 to  3 3" = DN43-D33,
        "-4 3 to  4 3" = DN43-D43,
        "-4 3 to  5 3" = DN43-D53,
        "-4 3 to  6 3" = DN43-D63,
        "-4 3 to  7 3" = DN43-D73,
        "-4 3 to  8 3" = DN43-D83,
        "-4 3 to  9 3" = DN43-D93,
        "-4 3 to  10 3" = DN43-D103,
        "-4 3 to  11 3" = DN43-D113,
        "-4 3 to  12 3" = DN43-D123,
        "-4 3 to  13 3" = DN43-D133,
        "-4 3 to  14 3" = DN43-D143,
        "-3 3 to  -2 3" = DN33-DN23,
        "-3 3 to  -1 3" = DN33-DN13,
        "-3 3 to  0 3" = DN33-D03,
        "-3 3 to  1 3" = DN33-D13,
        "-3 3 to  2 3" = DN33-D23,
        "-3 3 to  3 3" = DN33-D33,
        "-3 3 to  4 3" = DN33-D43,
        "-3 3 to  5 3" = DN33-D53,
        "-3 3 to  6 3" = DN33-D63,
        "-3 3 to  7 3" = DN33-D73,
        "-3 3 to  8 3" = DN33-D83,
        "-3 3 to  9 3" = DN33-D93,
        "-3 3 to  10 3" = DN33-D103,
        "-3 3 to  11 3" = DN33-D113,
        "-3 3 to  12 3" = DN33-D123,
        "-3 3 to  13 3" = DN33-D133,
        "-3 3 to  14 3" = DN33-D143,
        "-2 3 to  -1 3" = DN23-DN13,
        "-2 3 to  0 3" = DN23-D03,
        "-2 3 to  1 3" = DN23-D13,
        "-2 3 to  2 3" = DN23-D23,
        "-2 3 to  3 3" = DN23-D33,
        "-2 3 to  4 3" = DN23-D43,
        "-2 3 to  5 3" = DN23-D53,
        "-2 3 to  6 3" = DN23-D63,
        "-2 3 to  7 3" = DN23-D73,
        "-2 3 to  8 3" = DN23-D83,
        "-2 3 to  9 3" = DN23-D93,
        "-2 3 to  10 3" = DN23-D103,
        "-2 3 to  11 3" = DN23-D113,
        "-2 3 to  12 3" = DN23-D123,
        "-2 3 to  13 3" = DN23-D133,
        "-2 3 to  14 3" = DN23-D143,
        "-1 3 to  0 3" = DN13-D03,
        "-1 3 to  1 3" = DN13-D13,
        "-1 3 to  2 3" = DN13-D23,
        "-1 3 to  3 3" = DN13-D33,
        "-1 3 to  4 3" = DN13-D43,
        "-1 3 to  5 3" = DN13-D53,
        "-1 3 to  6 3" = DN13-D63,
        "-1 3 to  7 3" = DN13-D73,
        "-1 3 to  8 3" = DN13-D83,
        "-1 3 to  9 3" = DN13-D93,
        "-1 3 to  10 3" = DN13-D103,
        "-1 3 to  11 3" = DN13-D113,
        "-1 3 to  12 3" = DN13-D123,
        "-1 3 to  13 3" = DN13-D133,
        "-1 3 to  14 3" = DN13-D143,
        "0 3 to  1 3" = D03-D13,
        "0 3 to  2 3" = D03-D23,
        "0 3 to  3 3" = D03-D33,
        "0 3 to  4 3" = D03-D43,
        "0 3 to  5 3" = D03-D53,
        "0 3 to  6 3" = D03-D63,
        "0 3 to  7 3" = D03-D73,
        "0 3 to  8 3" = D03-D83,
        "0 3 to  9 3" = D03-D93,
        "0 3 to  10 3" = D03-D103,
        "0 3 to  11 3" = D03-D113,
        "0 3 to  12 3" = D03-D123,
        "0 3 to  13 3" = D03-D133,
        "0 3 to  14 3" = D03-D143,
        "1 3 to  2 3" = D13-D23,
        "1 3 to  3 3" = D13-D33,
        "1 3 to  4 3" = D13-D43,
        "1 3 to  5 3" = D13-D53,
        "1 3 to  6 3" = D13-D63,
        "1 3 to  7 3" = D13-D73,
        "1 3 to  8 3" = D13-D83,
        "1 3 to  9 3" = D13-D93,
        "1 3 to  10 3" = D13-D103,
        "1 3 to  11 3" = D13-D113,
        "1 3 to  12 3" = D13-D123,
        "1 3 to  13 3" = D13-D133,
        "1 3 to  14 3" = D13-D143,
        "2 3 to  3 3" = D23-D33,
        "2 3 to  4 3" = D23-D43,
        "2 3 to  5 3" = D23-D53,
        "2 3 to  6 3" = D23-D63,
        "2 3 to  7 3" = D23-D73,
        "2 3 to  8 3" = D23-D83,
        "2 3 to  9 3" = D23-D93,
        "2 3 to  10 3" = D23-D103,
        "2 3 to  11 3" = D23-D113,
        "2 3 to  12 3" = D23-D123,
        "2 3 to  13 3" = D23-D133,
        "2 3 to  14 3" = D23-D143,
        "3 3 to  4 3" = D33-D43,
        "3 3 to  5 3" = D33-D53,
        "3 3 to  6 3" = D33-D63,
        "3 3 to  7 3" = D33-D73,
        "3 3 to  8 3" = D33-D83,
        "3 3 to  9 3" = D33-D93,
        "3 3 to  10 3" = D33-D103,
        "3 3 to  11 3" = D33-D113,
        "3 3 to  12 3" = D33-D123,
        "3 3 to  13 3" = D33-D133,
        "3 3 to  14 3" = D33-D143,
        "4 3 to  5 3" = D43-D53,
        "4 3 to  6 3" = D43-D63,
        "4 3 to  7 3" = D43-D73,
        "4 3 to  8 3" = D43-D83,
        "4 3 to  9 3" = D43-D93,
        "4 3 to  10 3" = D43-D103,
        "4 3 to  11 3" = D43-D113,
        "4 3 to  12 3" = D43-D123,
        "4 3 to  13 3" = D43-D133,
        "4 3 to  14 3" = D43-D143,
        "5 3 to  6 3" = D53-D63,
        "5 3 to  7 3" = D53-D73,
        "5 3 to  8 3" = D53-D83,
        "5 3 to  9 3" = D53-D93,
        "5 3 to  10 3" = D53-D103,
        "5 3 to  11 3" = D53-D113,
        "5 3 to  12 3" = D53-D123,
        "5 3 to  13 3" = D53-D133,
        "5 3 to  14 3" = D53-D143,
        "6 3 to  7 3" = D63-D73,
        "6 3 to  8 3" = D63-D83,
        "6 3 to  9 3" = D63-D93,
        "6 3 to  10 3" = D63-D103,
        "6 3 to  11 3" = D63-D113,
        "6 3 to  12 3" = D63-D123,
        "6 3 to  13 3" = D63-D133,
        "6 3 to  14 3" = D63-D143,
        "7 3 to  8 3" = D73-D83,
        "7 3 to  9 3" = D73-D93,
        "7 3 to  10 3" = D73-D103,
        "7 3 to  11 3" = D73-D113,
        "7 3 to  12 3" = D73-D123,
        "7 3 to  13 3" = D73-D133,
        "7 3 to  14 3" = D73-D143,
        "8 3 to  9 3" = D83-D93,
        "8 3 to  10 3" = D83-D103,
        "8 3 to  11 3" = D83-D113,
        "8 3 to  12 3" = D83-D123,
        "8 3 to  13 3" = D83-D133,
        "8 3 to  14 3" = D83-D143,
        "9 3 to 10 3" = D93-D103,
        "9 3 to 11 3" = D93-D113,
        "9 3 to 12 3" = D93-D123,
        "9 3 to 13 3" = D93-D133,
        "9 3 to 14 3" = D93-D143,
        "10 3 to 11 3" = D103-D113,
        "10 3 to 12 3" = D103-D123,
        "10 3 to 13 3" = D103-D133,
        "10 3 to 14 3" = D103-D143,
        "11 3 to  12 3" = D113-D123,
        "11 3 to  13 3" = D113-D133,
        "11 3 to  14 3" = D113-D143,
        "12 3 to 13 3" = D123-D133,
        "12 3 to 14 3" = D123-D143,
        "13 3 to 14 3" = D133-D143
       )

str(pwpp_comparisons)
```

#### Post-hoc Test

Used the `r contrast` function with `r method` specified to be my named list.

```{r}
lm_2_posthoc_comparisons <- contrast(lm_2_posthoc_means, method = pwpp_comparisons, adjust = "sidak")
lm_2_posthoc_comparisons
```

#### Compact Letter Display

```{r}
lm_2_posthoc_forcld <- emmeans(lm_2, ~ day_fac:age)
lm_2_posthoc_forcld

lm_2_posthoc_cld <- multcomp::cld(lm_2_posthoc_forcld, alpha = 0.05, Letters = LETTERS, adjust = "sidak")
lm_2_posthoc_cld
```

```{r}
lm_2_posthoc_cld_nospaces <- 
  lm_2_posthoc_cld %>% 
    mutate(across(where(is.character), str_remove_all, pattern = fixed(" ")))

syrup_vol_data_fil_letters <- syrup_vol_data_fil %>% 
  group_by(day_fac, age) %>% 
  summarise(mean = mean(volume24_corr), se = (sd(volume24_corr)/sqrt(10))) %>% 
  inner_join(lm_2_posthoc_cld_nospaces) 


syrup_vol_data_fil_letters$letters <- syrup_vol_data_fil_letters$.group
syrup_vol_data_fil_letters

syrup_vol_data_fil_letters %>% 
  ggplot(aes(day_fac, mean, color=age, group=1)) +
  
  geom_point()+
  stat_summary(fun=sum, geom="line")+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2,
                 position=position_dodge(0.05))+
  geom_text(aes(x= day_fac, y=0.1 + mean + se,label=letters, angle = 90),hjust=0)+
  theme_classic() +
  
  theme(
    text = element_text(size = 14), 
    axis.title.x=element_text(),
    axis.text.x = element_text(vjust=0.3, size = 12, color="black"), 
    axis.ticks.x=element_blank(),
    axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
    axis.text.y = element_text(color="black", size = 10),
    strip.placement = "outside", 
    strip.text.x = element_text( #text in facet labels
      size = 12, color = "black", face = "bold"),
    strip.background = element_rect(#background of facet labels
      color="white", fill="#ffffff", size=1.5),
    panel.spacing.y = unit(2, "lines"),
    legend.position = "none")+
    scale_color_manual(values=c("#60435F", "#5EB1BF"))+
    scale_y_continuous(name ="Average Volume of Syrup \nConsumed Over 24h (mL)")+
    xlab("Day")+
    facet_wrap(~ age)
```

#### Pairwise P-value Plot

```{r}
lm_2_posthoc_fig <- emmeans(lm_2, ~day_fac:age)
lm_2_posthoc_fig
```

```{r}
pwpp_fig <- 
  pwpp(lm_2_posthoc_fig, method = pwpp_comparisons, adjust = "sidak", type = "response", sort = FALSE, ylab = "Day-Age Combination", xlab = "P-value")+
  ggplot2::theme_classic()+
  ggplot2::theme(
    axis.text.x = element_text(color="black"), 
    axis.text.y = element_text(color="black"),
    panel.grid.major.y = element_line(colour="grey80", size=0.3)
  )+
  ggplot2::geom_hline(yintercept = 20.5, linetype = "dashed")+
  facet_zoom(xlim = c(-0.05, 0.63), zoom.size = 1)
  
pwpp_fig

```
